---
title: "TSP for Brazilian State Capitals"
author: Dan S. Reznik
date: Abril, 2019
output: 
  html_document:
    mathjax: null
    toc: true
    toc_depth: 3
    toc_float: true
    theme: united
    df_print: paged
    highlight: tango
    code_folding: show
---

This project's [repo](https://github.com/dan-reznik/TSP-Brazilian-Capitals)

```{r,echo=F}
knitr::opts_chunk$set(
  cache=T,
  collapse=T,
  comment="#>",
  dpi=96,
  out.width='100%'
)
```

### Load libraries

```{r,message=F}
library(tidyverse)
library(tspmeta)
library(ggmap)
library(sp)
library(stringi)
library(gridExtra)
library(grid)
detach("package:dplyr", character.only = TRUE)
library("dplyr", character.only = TRUE) # MASS::select() conflict
library(maptools)
source("tsp_utils.R")
```

### Get brazilian capitals [lat/lon](http://relogiosdesol.blogspot.com.br/2009/11/coordenadas-geograficas-das-capitas-dos.html)

```{r,message=F}
capitais <- read_csv("data/capitais.csv")
```

### Construct a TSP object.

Returns TSP solver methods

```{r}
get_solvers()
```

Specifies TSP engine's full path

```{r}
# TSP::concorde_path("./concorde")
TSP::concorde_path(getwd() %s+% "/../concorde")
```

Tests `concorde` and `2-opt` methods in point lattice

```{r}
test_df <- tibble(x=seq(0,1,.1),y=seq(0,1,.1))%>%expand(x,y)
test_tour <- get_tour(test_df,method="concorde")
test_tour_2_opt <- get_tour(test_df,method="2-opt")
```

Plots found tours

```{r}
p1 <- plot_tour(test_df,test_tour,"red","concorde")
p2 <- plot_tour(test_df,test_tour_2_opt,"green","2-opt")
grid.arrange(p1, p2, ncol = 2)
```

```{r,include=F}
{
  p12 <- arrangeGrob(p2,p1,ncol=2) #generates g
  ggsave("./pics/tsp 2-opt vs concorde.png",p12) #,width=10,height=10)
}
```

### Brazilian Capitals Tour

Start tour at Rio's index

```{r}
capitais%>%filter(uf=="RJ")
```

Compute state capital tour using `2-opt` and `concorde` methods

Note: seems "start" is being ignored by concorde

```{r}
capitais_tsp_2_opt <- get_tour(capitais%>%select(x=lon_dec,y=lat_dec),
                               method="2-opt")
capitais_tsp <- get_tour(capitais%>%select(x=lon_dec,y=lat_dec),
                         method="concorde",
                         start=22)

capitais_tsp_prep_2_opt <- process_tour(capitais_tsp_2_opt,capitais)
capitais_tsp_prep <- process_tour(capitais_tsp,capitais)
```

Plot the results

```{r}
b1 <- plot_tour(capitais%>%select(x=lon_dec,y=lat_dec),
                capitais_tsp,"red","concorde")
b2 <- plot_tour(capitais%>%select(x=lon_dec,y=lat_dec),
                capitais_tsp_2_opt,"green","2-opt")
grid.arrange(b2, b1, ncol = 2)
```

```{r,include=F}
{
  b12 <- arrangeGrob(b2,b1,ncol=2) #generates g
  ggsave("./pics/tsp 2-opt vs concorde brasil.png",b12) #,width=10,height=10)
}
```

Load Brazil shape file

```{r,message=F,}
# area <- readShapePoly("data/BRUFE250GC_SIR.shp") %>% fortify
area <- rgdal::readOGR('data/BRUFE250GC_SIR.shp') %>% fortify
```

Show `concorde` path in blue and `2-opt` path (somewhat jittered) in green.

```{r}
area %>%
  ggplot(aes(x = long, y = lat)) +
  geom_polygon(aes(group=group),fill=NA,color="gray",size=I(1)) +
  geom_polygon(aes(lon_dec,lat_dec),
          color="blue",fill=NA,
          data=capitais_tsp_prep) +
    geom_polygon(aes(lon_dec,lat_dec),
          color="green",fill=NA,
          position=position_jitter(1),
          data=capitais_tsp_prep_2_opt) +
  geom_point(aes(lon_dec,lat_dec),
             color = "red", size = 2,
             data = capitais) +
  geom_text(aes(lon_dec,lat_dec,label=cidade),
            data=capitais,vjust=-1,size=3) +
  labs(x = "Longitude", y = "Latitude") +
  coord_fixed()
```

```{r,include=F}
ggsave("./pics/tsp brazil ibge state polygons.png",height=10,width=10)
```
